### 2014-03-05 paper/designspace.tex
minor modifications

While possible to create, a tube which is open on the user side and closed on the system side is outside our focus is on computer-mediated interaction, and we therefore do not discuss these tubes.

>>>>

While possible to create, a tube which is open on the user side and closed on the system side is outside our focus on computer-mediated interaction, and we therefore do not discuss these tubes.

### 2014-03-05 paper/tubes.tex
minor modifications

This is a relaxed version of the Chinese Postman Problem\footnote{\url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If inputted path components are disconnected, we must create edges that connect them; additionally we can create edges to connect odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be shielded by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).

@@

We need to connect disconnected subgraphs in $G$.  Let $G_{dis} = \{G_1, G_2, ... G_n\} \in G$ s.t. $\cup{\{G_i \in G_{dis}\}} = G$ and $G_i \cap G_j  = \{ \} \forall G_i, G_j \in G_{dis}, i\neq j$ be disconnected subgraphs in G.  Create $E_{conn} = \{e = (u, v), u \in G_i, v \in G_j, i \neq j, weight(e) = distance(u, v)\}$ be a set of edges.  Sort $E_{conn}$ s.t. $E_{conn} = \{e_1, e_2, ... e_n\}, weight(e_1) \leq weight(e_2) \leq \ldots \leq weight(e_n)$.  Let $E_{conn-min} = \{ \}$.

@@

>>>>

This is a relaxed version of the Chinese Postman Problem\footnote{\url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If inputted path components are disconnected, we must create edges that connect them; additionally we can create new edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be shielded by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).

@@

We need to connect disconnected subgraphs in $G$.  Let $G_{dis} = \{G_1, G_2, ... G_n\} \in G$ s.t. $\cup{\{G_i \in G_{dis}\}} = G$ and $G_i \cap G_j  = \{ \} \forall G_i, G_j \in G_{dis}, i\neq j$ be disconnected subgraphs in G.  Create $E_{conn} = \{e = (u, v), u \in G_i, v \in G_j, i \neq j, weight(e) = distance(u, v)\}$ be a set of edges.  Sort $E_{conn}$ s.t. $E_{conn} = \{e_1, e_2, ... e_n\}, weight(e_1) \leq weight(e_2) \leq \ldots \leq weight(e_n)$.  Let $E_{conn-min} = \{ \}$. \valkyrie{another approach to this that actually would minimize it is to reduce each disconnected subgraph to a single point with one edge going to each other disconnected subgraph-point.  these edges' weights would be the lowest weight of any edge connecting any points in the two subgraphs.  by finding a minimum matching on these subgraph points, I think we will get the best answer.}

@@

Once we have a semi-Eulerian graph, we need to create an Euler tour.  An Euler tour is a path that touches every edge once, beginning and ending at the two nodes of odd degree: in this case, those are the user-selected start and end nodes.  We use a sligh modification of Fleury's algorithm\footnote{\url{http://en.wikipedia.org/wiki/Eulerian_path\#Fleury.27s_algorithm}} for this, where instead of randomly selecting from non-bridge paths at each node, we select the path which turns the least from the most recent path (i.e., we prefer to pass straight through a node, if possible).  This minimizes turns in the final artifact, which eases support material removal and assembly.
